Prison Data Analysis

### 2019-07-25 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData-LogTrans-results.Rmd
Continued with the prison data analysis - Fitted TS-regression models

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "OLS")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
  ggtitle("OLS Vs Base (Biased)")

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
  ggtitle("OLS Vs Base (Unbiased)")

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
  ggtitle("MinT(Shrink) Vs Base (Biased)")

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
  ggtitle("MinT(Shrink) Vs Base (Unbiased)")

@@

>>>>

```{r}

# Avg_MSE_Base <- Avg_MSE %>% 
#   filter(`R-method` == "Base") %>% 
#   ungroup() %>% 
#   mutate(`F-method` = recode(`F-method`, "ARIMA_bias"= "Bias", "ARIMA_unbias" = "Unbiase"))
# 
# Avg_MSE_MinT <- Avg_MSE %>% 
#   filter(`R-method` == "MinT(Shrink)") %>% 
#   ungroup() %>% 
#   mutate(`F-method` = recode(`F-method`, "ARIMA_bias"= "Bias", "ARIMA_unbias" = "Unbiase")) 
# 
# 
# Avg_MSE_Base %>% 
#   ggplot(aes(x = Forecast_Horizon, y = MSE, color = `F-method`, shape = `F-method`)) + 
#   geom_point(size = 3) + 
#   scale_color_manual(values = c("Green", "Red")) +
#   scale_shape_manual(values=0:1) + 
#   geom_point(data = Avg_MSE_MinT, aes(x = Forecast_Horizon, y = MSE, 
#                                       color = `F-method`, shape = `F-method`), size = 3) + 
#   scale_shape_manual(values=2:3) +
#   geom_line()

@@

```{r echo=FALSE}
DF_MSE <- DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1", "2" = "h=2", "3"= "h=3", "4" = "h=4"))

DF_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)")) %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)` ) %>% 
  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`) %>% 
  gather(`Base-MinT`, `Base-OLS`, key = Method, value = MSE) %>% 
  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`)

# DF %>% 
#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
#   summarise(MSE = mean(SquaredE)) %>% 
#   filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "OLS")) %>% 
#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
#   geom_line() + 
#   facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
#   ggtitle("OLS Vs Base (Biased)")
# 
# DF %>% 
#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
#   summarise(MSE = mean(SquaredE)) %>% 
#   filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS")) %>% 
#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
#   geom_line() + 
#   facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
#   ggtitle("OLS Vs Base (Unbiased)")
# 
# DF %>% 
#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
#   summarise(MSE = mean(SquaredE)) %>% 
#   filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
#   geom_line() + 
#   facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
#   ggtitle("MinT(Shrink) Vs Base (Biased)")
# 
# DF %>% 
#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
#   summarise(MSE = mean(SquaredE)) %>% 
#   filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
#   geom_line() + 
#   facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
#   ggtitle("MinT(Shrink) Vs Base (Unbiased)")

\newpage
